---
title: "Pre-Post Questions: Mehrkam Project"
author: Odalys Barrientos
output: html_notebook
---

```{r}
library(readr)
MehrkamData <- read_csv("~/Documents/MA321-FA21/MehrkamProject/Data/Mehrkam-CleanData.csv")

#View(MehrkamData)

```

# Reverse Code: Pre 1
```{r}
Pre1 <- vector()

for(i in 1:length(MehrkamData$Pre_Q1)){
  if(MehrkamData$Pre_Q1[i] == 7){
  Pre1[i] <- 1
}
  if(MehrkamData$Pre_Q1[i] == 6){
  Pre1[i] <- 2
}
  if(MehrkamData$Pre_Q1[i] == 5){
  Pre1[i] <- 3
}
  if(MehrkamData$Pre_Q1[i] == 3){
  Pre1[i] <- 5
}
  if(MehrkamData$Pre_Q1[i] == 2){
  Pre1[i] <- 6
}
  if(MehrkamData$Pre_Q1[i] == 1){
  Pre1[i] <- 7
  }
  if(MehrkamData$Pre_Q1[i] == 4){
  Pre1[i] <- 4
  }
  }
Pre1
```


# Reverse Code: Pre 2
```{r}
Pre2 <- vector()

for(i in 1:length(MehrkamData$Pre_Q2)){
  if(MehrkamData$Pre_Q2[i] == 7){
  Pre2[i] <- 1
}
  if(MehrkamData$Pre_Q2[i] == 6){
  Pre2[i] <- 2
}
  if(MehrkamData$Pre_Q2[i] == 5){
  Pre2[i] <- 3
}
  if(MehrkamData$Pre_Q2[i] == 3){
  Pre2[i] <- 5
}
  if(MehrkamData$Pre_Q2[i] == 2){
  Pre2[i] <- 6
}
  if(MehrkamData$Pre_Q2[i] == 1){
  Pre2[i] <- 7
  }
  if(MehrkamData$Pre_Q2[i] == 4){
  Pre2[i] <- 4
  }
  }
Pre2
```

# Reverse Code: Pre 3
```{r}
Pre3 <- vector()

for(i in 1:length(MehrkamData$Pre_Q3)){
  if(MehrkamData$Pre_Q3[i] == 7){
  Pre3[i] <- 1
}
  if(MehrkamData$Pre_Q3[i] == 6){
  Pre3[i] <- 2
}
  if(MehrkamData$Pre_Q3[i] == 5){
  Pre3[i] <- 3
}
  if(MehrkamData$Pre_Q3[i] == 3){
  Pre3[i] <- 5
}
  if(MehrkamData$Pre_Q3[i] == 2){
  Pre3[i] <- 6
}
  if(MehrkamData$Pre_Q3[i] == 1){
  Pre3[i] <- 7
  }
  if(MehrkamData$Pre_Q3[i] == 4){
  Pre3[i] <- 4
  }
  }
Pre3
```

# Reverse Code: Pre 9
```{r}
Pre9 <- vector()

for(i in 1:length(MehrkamData$Pre_Q9)){
  if(MehrkamData$Pre_Q9[i] == 7){
  Pre9[i] <- 1
}
  if(MehrkamData$Pre_Q9[i] == 6){
  Pre9[i] <- 2
}
  if(MehrkamData$Pre_Q9[i] == 5){
  Pre9[i] <- 3
}
  if(MehrkamData$Pre_Q9[i] == 3){
  Pre9[i] <- 5
}
  if(MehrkamData$Pre_Q9[i] == 2){
  Pre9[i] <- 6
}
  if(MehrkamData$Pre_Q9[i] == 1){
  Pre9[i] <- 7
  }
  if(MehrkamData$Pre_Q9[i] == 4){
  Pre9[i] <- 4
  }
  }
Pre9
```
# Reverse Code: Pre 10
```{r}
Pre10 <- vector()

for(i in 1:length(MehrkamData$Pre_Q10)){
  if(MehrkamData$Pre_Q10[i] == 7){
  Pre10[i] <- 1
}
  if(MehrkamData$Pre_Q10[i] == 6){
  Pre10[i] <- 2
}
  if(MehrkamData$Pre_Q10[i] == 5){
  Pre10[i] <- 3
}
  if(MehrkamData$Pre_Q10[i] == 3){
  Pre10[i] <- 5
}
  if(MehrkamData$Pre_Q10[i] == 2){
  Pre10[i] <- 6
}
  if(MehrkamData$Pre_Q10[i] == 1){
  Pre10[i] <- 7
  }
  if(MehrkamData$Pre_Q10[i] == 4){
  Pre10[i] <- 4
  }
  }
Pre10
```

# Reverse Code: Pre 11
```{r}
Pre11 <- vector()

for(i in 1:length(MehrkamData$Pre_Q11)){
  if(MehrkamData$Pre_Q11[i] == 7){
  Pre11[i] <- 1
}
  if(MehrkamData$Pre_Q11[i] == 6){
  Pre11[i] <- 2
}
  if(MehrkamData$Pre_Q11[i] == 5){
  Pre11[i] <- 3
}
  if(MehrkamData$Pre_Q11[i] == 3){
  Pre11[i] <- 5
}
  if(MehrkamData$Pre_Q11[i] == 2){
  Pre11[i] <- 6
}
  if(MehrkamData$Pre_Q11[i] == 1){
  Pre11[i] <- 7
  }
  if(MehrkamData$Pre_Q11[i] == 4){
  Pre11[i] <- 4
  }
  }
Pre11
```

# Reverse Code: Pre 13
```{r}
Pre13 <- vector()

for(i in 1:length(MehrkamData$Pre_Q13)){
  if(MehrkamData$Pre_Q13[i] == 7){
  Pre13[i] <- 1
}
  if(MehrkamData$Pre_Q13[i] == 6){
  Pre13[i] <- 2
}
  if(MehrkamData$Pre_Q13[i] == 5){
  Pre13[i] <- 3
}
  if(MehrkamData$Pre_Q13[i] == 3){
  Pre13[i] <- 5
}
  if(MehrkamData$Pre_Q13[i] == 2){
  Pre13[i] <- 6
}
  if(MehrkamData$Pre_Q13[i] == 1){
  Pre13[i] <- 7
  }
  if(MehrkamData$Pre_Q13[i] == 4){
  Pre13[i] <- 4
  }
  }
Pre13
```

# Reverse Code: Pre 14
```{r}
Pre14 <- vector()

for(i in 1:length(MehrkamData$Pre_Q14)){
  if(MehrkamData$Pre_Q14[i] == 7){
  Pre14[i] <- 1
}
  if(MehrkamData$Pre_Q14[i] == 6){
  Pre14[i] <- 2
}
  if(MehrkamData$Pre_Q14[i] == 5){
  Pre14[i] <- 3
}
  if(MehrkamData$Pre_Q14[i] == 3){
  Pre14[i] <- 5
}
  if(MehrkamData$Pre_Q14[i] == 2){
  Pre14[i] <- 6
}
  if(MehrkamData$Pre_Q14[i] == 1){
  Pre14[i] <- 7
  }
  if(MehrkamData$Pre_Q14[i] == 4){
  Pre14[i] <- 4
  }
  }
Pre14
```


# Reverse Code: Post 1
```{r}
Post8 <- vector()

for(i in 1:length(MehrkamData$Post_Q1)){
  if(MehrkamData$Post_Q1[i] == 7){
  Post8[i] <- 1
}
  if(MehrkamData$Post_Q1[i] == 6){
  Post8[i] <- 2
}
  if(MehrkamData$Post_Q1[i] == 5){
  Post8[i] <- 3
}
  if(MehrkamData$Post_Q1[i] == 3){
  Post8[i] <- 5
}
  if(MehrkamData$Post_Q1[i] == 2){
  Post8[i] <- 6
}
  if(MehrkamData$Post_Q1[i] == 1){
  Post8[i] <- 7
  }
  if(MehrkamData$Post_Q1[i] == 4){
  Post8[i] <- 4
  }
  }
Post8
```

# Reverse Code: Post 2
```{r}
Post15 <- vector()

for(i in 1:length(MehrkamData$Post_Q2)){
  if(MehrkamData$Post_Q2[i] == 7){
  Post15[i] <- 1
}
  if(MehrkamData$Post_Q2[i] == 6){
  Post15[i] <- 2
}
  if(MehrkamData$Post_Q2[i] == 5){
  Post15[i] <- 3
}
  if(MehrkamData$Post_Q2[i] == 3){
  Post15[i] <- 5
}
  if(MehrkamData$Post_Q2[i] == 2){
  Post15[i] <- 6
}
  if(MehrkamData$Post_Q2[i] == 1){
  Post15[i] <- 7
  }
  if(MehrkamData$Post_Q2[i] == 4){
  Post15[i] <- 4
  }
  }
Post15
```

# Reverse Code: Post 3
```{r}
Post1 <- MehrkamData$Post_Q3

Post1
```

# Reverse Code: Post 4
```{r}
Post6 <- vector()

for(i in 1:length(MehrkamData$Post_Q4)){
  if(MehrkamData$Post_Q4[i] == 7){
  Post6[i] <- 1
}
  if(MehrkamData$Post_Q4[i] == 6){
  Post6[i] <- 2
}
  if(MehrkamData$Post_Q4[i] == 5){
  Post6[i] <- 3
}
  if(MehrkamData$Post_Q4[i] == 3){
  Post6[i] <- 5
}
  if(MehrkamData$Post_Q4[i] == 2){
  Post6[i] <- 6
}
  if(MehrkamData$Post_Q4[i] == 1){
  Post6[i] <- 7
  }
  if(MehrkamData$Post_Q4[i] == 4){
  Post6[i] <- 4
  }
  }
Post6
```

# Reverse Code: Post 5
```{r}
Post12 <- MehrkamData$Post_Q5

Post12
```

# Reverse Code: Post 6
```{r}
Post13 <- MehrkamData$Post_Q6

Post13
```

# Reverse Code: Post 7
```{r}
Post4 <- MehrkamData$Post_Q7

Post4
```

# Reverse Code: Post 8
```{r}
Post10 <- MehrkamData$Post_Q8

Post10
```
# Reverse Code: Post 9
```{r}
Post2 <- MehrkamData$Post_Q9

Post2
```

# Reverse Code: Post 10
```{r}
Post5 <- vector()

for(i in 1:length(MehrkamData$Post_Q10)){
  if(MehrkamData$Post_Q10[i] >= 7){
  Post5[i] <- 1
}
  if(MehrkamData$Post_Q10[i] == 6){
  Post5[i] <- 2
}
  if(MehrkamData$Post_Q10[i] == 5){
  Post5[i] <- 3
}
  if(MehrkamData$Post_Q10[i] == 3){
  Post5[i] <- 5
}
  if(MehrkamData$Post_Q10[i] == 2){
  Post5[i] <- 6
}
  if(MehrkamData$Post_Q10[i] == 1){
  Post5[i] <- 7
  }
  if(MehrkamData$Post_Q10[i] == 4){
  Post5[i] <- 4
  }
  }
Post5
```
# Reverse Code: Post 11
```{r}
Post9 <- MehrkamData$Post_Q11

Post9
```

# Reverse Code: Post 12
```{r}
Post7 <- vector()

for(i in 1:length(MehrkamData$Post_Q12)){
  if(MehrkamData$Post_Q12[i] >= 7){
  Post7[i] <- 1
}
  if(MehrkamData$Post_Q12[i] == 6){
  Post7[i] <- 2
}
  if(MehrkamData$Post_Q12[i] == 5){
  Post7[i] <- 3
}
  if(MehrkamData$Post_Q12[i] == 3){
  Post7[i] <- 5
}
  if(MehrkamData$Post_Q12[i] == 2){
  Post7[i] <- 6
}
  if(MehrkamData$Post_Q12[i] == 1){
  Post7[i] <- 7
  }
  if(MehrkamData$Post_Q12[i] == 4){
  Post7[i] <- 4
  }
  }
Post7
```
# Reverse Code: Post 13
```{r}
Post3 <- MehrkamData$Post_Q13

Post3
```



# Reverse Code: Post 14
```{r}
Post11 <- vector()

for(i in 1:length(MehrkamData$Post_Q14)){
  if(MehrkamData$Post_Q14[i] >= 7){
  Post11[i] <- 1
}
  if(MehrkamData$Post_Q14[i] == 6){
  Post11[i] <- 2
}
  if(MehrkamData$Post_Q14[i] == 5){
  Post11[i] <- 3
}
  if(MehrkamData$Post_Q14[i] == 3){
  Post11[i] <- 5
}
  if(MehrkamData$Post_Q14[i] == 2){
  Post11[i] <- 6
}
  if(MehrkamData$Post_Q14[i] == 1){
  Post11[i] <- 7
  }
  if(MehrkamData$Post_Q14[i] == 4){
  Post11[i] <- 4
  }
  }
Post11
```

# Reverse Code: Post 15
```{r}
Post14 <- MehrkamData$Post_Q15

Post14
```

# NEW DATA
```{r}
SurveyOutcomes <- data.frame(Conditions = MehrkamData$Condition, Pre1 = Pre1, Pre2 =Pre2, Pre3 =Pre3, Pre4 =MehrkamData$Pre_Q4, Pre5 = MehrkamData$Pre_Q5, Pre6 = MehrkamData$Pre_Q6, Pre7 = MehrkamData$Pre_Q7, Pre8 = MehrkamData$Pre_Q8, Pre9 =Pre9, Pre10 = Pre10, Pre11 = Pre11, Pre12 = MehrkamData$Pre_Q12, Pre13 = Pre13, Pre14 = Pre14, Pre15 = MehrkamData$Pre_Q15, Post1, Post2, Post3,Post4, Post5, Post6, Post7, Post8, Post9, Post10,Post11, Post12, Post13, Post14, Post15 )

#View(SurveyOutcomes)

#write.csv(SurveyOutcomes, "SurveyOutcomes.csv" )

```

